---
title: |
 \textcolor[RGB]{34,139,34}{\textbf{Workshop on Integrating R and Google Forms}}
author: |
        | <font size="4">**Gilvan Guedes** (grguedes@epopea.com.br)</font>
        | <font size="4">**Jeferson Andrade** (jeferson@epopea.com.br)</font>
date: |
      | Cedeplar, Universidade Federal de Minas Gerais
      | 09 March 2020 - Belo Horizonte, Brazil
output: pdf_document
fontsize: 14pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intructions for accessing the workshop project from EPOPEA Github

Follow the steps above:

* First, open RStudio on your computer as an administrator:

  + If you are a Windows user, right click on RStudio and Select ``Open as administrator``
  + If you are a Mac of Linux user:
  
    + Go to <tt>`Applications`</tt>
    + Right click on RStudio and select <tt>`Show Package Contents`</tt>
    + Go to Contents/MacOS
    + Now open <tt>`Terminal`</tt> (in bash mode)
    + Type <tt>`sudo`</tt> and drag the RStudio.exec into <tt>`Applications`</tt>
    + Press on ENTER
    
* Then click on <tt>`File`</tt> $\rightarrow$ \texttt{New Project...} $\rightarrow$ \texttt{Version Control} $\rightarrow$ <tt>`Git`</tt>
* In the first **text block** (Repository URL the following code) insert: <https://github.com/epopea/workshop.git>
* The second **text block** will be automatically filled
* In the thir **text block** select ``Browser`` and choose the folder where you want everything to be saved. In our case, we have chosen a folder where the Git was installed: <tt>`/Library/Developer/CommandLineTools/usr/share/git-core/perl/Git`</tt>
* After choosing the sub-folder, just click on the button **Create Project**.

Now you should be able to see the workshop folder loaded in the <tt>`Files`</tt> tab of RStudio

* Click on the \texttt{R and Google Forms} folder
* Click on the \texttt{Integrando Google Sheets com R.R} file to be loaded
* Click on the \texttt{Organizando o Banco de Dados.R} file to be loaded
* **Note**: If you want be able to change your working directory directly in RStudio, you should either:

  + Open RStudio without administrator privileges and leaving the third **text block** as the default while creating the New Project
  + Open RStudio with administrator privileges but choose, in the third **text block**, a folder that does not request the level of privilege as administrator, such as <tt>`/Users/grguedes/Documents`</tt>.
  
# Changing the working directory directly into RStudio

If you want to change your working directory directly into R, you will type:

* In \texttt{Windows}:

```{r r1}
#setwd("C:\\Users\\Usuário\\Downloads")
```

* In \texttt{Linux} or \texttt{MacOS}:

```{r r2}
#setwd("/Users/grguedes/Documents/")
```

Just remember to remove the \texttt{$\#$} symbol before the command so it will be activated.

Now, sit, relax and enjoy the Workshop!